---
title       : Check My Fit
subtitle    : Simple app to play around with linear fitting
author      : MattDSquared
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]     # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

--- &twocol

```{r setup, echo=FALSE, results='hide', message=FALSE}
library(ggplot2)
library(datasets); data(mtcars)
library(xtable)

conflvl <- .9

getConfInterval <- function(fit, xi, level) {
    sumCoef <- summary(fit)$coefficients
    sumCoef[xi,"Estimate"] + 
        c(-1,1) * qt(.5+level/2, df = fit$df) * sumCoef[xi,"Std. Error"]
}

myfit <- lm(mpg ~ wt, data=mtcars)

confInterval <- rbind(getConfInterval(myfit, 1, conflvl), 
                       getConfInterval(myfit, 2, conflvl))
```

## Why should I Check My Fit?

*** =left

* Ever wonder what it means to fit a line through some data?

* This app helps you learn it how it works!

*** =right

```{r slide1.plot, echo=FALSE, fig.height=6, fig.width=6}
gg <- ggplot(mtcars, aes(x=wt, y=mpg))
gg <- gg + geom_point(colour="steelblue", size=3) +
    labs(x="Weight [1000 lb]") +
    labs(y="Miles Per Gallon") + 
    labs(title=paste0("Find the slope and intercept for a best linear fit ", 
                      "through the data."))
alpha <- 37
beta <- -5.5
gg <- gg + geom_abline(intercept = alpha, slope = beta, 
                       colour = "red", size = 1.5)

gg <- gg + geom_smooth(method="lm", level=conflvl)

print(gg)
```

--- &twocol .class #id 

## Interactive User feedback

*** =left

* Better understand what that grey region is on ggplot2 smooth plots.

* Here's an example for a line with the form $y = A + B x$:

```{r example.line, echo=FALSE, results='asis'}
params.example <- data.frame(Fit = factor(c("Good","Bad")), 
                             A = c(38, 30), 
                             B = c(-5.7, -4))

tab.out <- xtable(params.example)

print(tab.out, type="html", include.rownames = FALSE)
```

* The app will let you know if you were close to the actual fit line by comparing the intercept (A) and slope (B) to the `r 100*conflvl`% confidence interval of these parameters.  

*** =right

```{r slide2.plot, echo=FALSE, fig.height=6, fig.width=6}
gg <- ggplot(mtcars, aes(x=wt, y=mpg))

gg <- gg + geom_point(colour="steelblue", size=3) +
    labs(x="Weight [1000 lb]") +
    labs(y="Miles Per Gallon") + 
    labs(title=sprintf(paste0("Tells user if line is inside a %d%% ",
                              "confidence bound."), 100*conflvl))

gg <- gg + 
    geom_abline(aes(colour="Good"), 
                       intercept=params.example[1,"A"], 
                       slope=params.example[1,"B"], 
                       data=, size = 1) +
    geom_abline(aes(colour="Bad"), 
                       intercept=params.example[2,"A"], 
                       slope=params.example[2,"B"], 
                       data=, size = 1) +
    scale_colour_discrete("")

gg <- gg + geom_smooth(aes(colour="BestFit"), method="lm", size = 1,
                       level=conflvl)

gg <- gg + theme(legend.position="right")

print(gg)
```

--- .class #id 

## How to use it

<img class=center src=assets/img/AppScreenshot.png height=450>

Simply start by guessing the intercept and slope in the input boxes, trying to minimize the means squared error (MSE) of the line. Then once you think you have it, click 'Check it', and the app will let you know how you did. 

--- .class #id 

## Where to go get it

* The app is hosted by shinyapps.io on my account:  
https://mattdsquared.shinyapps.io/CheckMyFit

* The source code can be found on my github account:  
https://github.com/MattDSquared/CheckMyFit

* The data used for this app is the classical mtcars data set built into R. 
